---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rpkgcameron

<!-- badges: start -->
<!-- badges: end -->

The goal of rpkgcameron is to make working with factors easier (and to get completion marks for my assignment!)

## Installation

You can install the released version of rpkgcameron from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rpkgcameron")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("camharris22/rpkgcameron")
```
## Demonstration

This is a basic example which shows you how to concatenate two factors:

```{r example}
library(rpkgcameron)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

As we can see, concatenate doesn't work properly here:

```{r cars}
c(a, b)
```

The function `fbind()` to the rescue!

```{r pressure, echo = FALSE}
fbind(a, b)
```


